---
title: "Logicals"
author: "Alex Vand"
date: "8/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Taking a look at `starwars`

- `include = `: to show or hide evverything
- `echo =`: show or hide code
- `eval = FALSE`: do not evaluate code chunk
- `warning = FALSE`: do not display code chunk


```{r, include = FALSE}
# summary of starwars
summary(starwars)

# look at first few lines
head(starwars)

# check out dimensions
dim(starwars)
```


```{r, warning = FALSE}
ggplot(data = starwars, aes(x = height, y = mass)) +
  geom_point(color = "purple")
```

## Find the mean, variance, and standard deviation of character height

```{r}
sw_height_mean <- mean(starwars$height, na.rm = TRUE)
# na.rm removes NA values
sw_height_mean

# Using similar naming, find:
# Variance fo character height
sw_height_var <- var(starwars$height, na.rm = TRUE)
sw_height_var # units: cm^2

# Standard deviation of character height
sw_height_sd <- sd(starwars$height, na.rm = TRUE)
sw_height_sd # unis: cm
```

Mean character height is `r round(sw_height_mean, 1)` cm, with a standard deviation of `r round(sw_height_sd, 1)` cm.

## Logical expressions

```{r}
5 < 10

"cat" > "armadillo"
"cat" > "elephant"
"cat" < "cats"
"dog" == "dog"
"f" < "z"
```

```{r}
10 <= 11

5 >= 4

3<= 1
```
```{r}
tarantulas <- c(1,3,7,10,15)

tarantulas > 5

```

## Logical operators
- `!`
- `&`
- `|`

```{r}
3 < 1 | 8 > 2

6 < 10 & 5 < 1

7 != 11

4 != 4 | 2 < 5 | 6 > 10

0 == FALSE
1 == TRUE
```




```{r}

```






